\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\usepackage{multicol}
\usepackage{lipsum}
\usepackage[hyperref]{}
\usepackage[scale=0.8, top=.7cm, bottom=.7cm, left=.8cm, right=.8cm]{geometry}

\usepackage[
    backend=biber,
    %defernumbers=true,
    sorting=ydnt]{biblatex}
\addbibresource{../../ags/meta/ags.bib}
\defbibenvironment{bibliography} 
  {\list
     {\printtext[labelnumberwidth]{% label format from numeric.bbx
        \printfield{labelprefix}%
        \printfield{labelnumber}}}
     {\setlength{\topsep}{0pt}% layout parameters from moderncvstyleclassic.sty
      \setlength{\labelwidth}{\hintscolumnwidth}%
      \setlength{\labelsep}{\separatorcolumnwidth}%
      \leftmargin\labelwidth%
      \advance\leftmargin\labelsep}%
      \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
  {\item}

\moderncvstyle{classic}
\moderncvcolor{black}
\setlength{\hintscolumnwidth}{3.5cm} 
\setlength{\makecvheadnamewidth}{10cm}

\definecolor{linkColor}{rgb}{0,0,0}
\newcommand{\itlink}[2]{\textcolor{linkColor}{\textit{\link[#1]{#2}}}}
\newcommand{\bfitlink}[2]{\textcolor{linkColor}{\textbf{\textit{\link[#1]{#2}}}}}
\newcommand{\hpref}[2]{\hyperref[#1]{\textcolor{linkColor}{\textit{#2}}}}

\firstname{Aleksei G.}
\familyname{Sorokin}
\email{asorokin@hawk.iit.edu}
\homepage{alegresor.github.io/}{}
%\social[linkedin][www.linkedin.com/in/aleksei-sorokin/]{linkedin.com/in/aleksei-sorokin}

\begin{document}
\makecvtitle
\vspace{-1.3cm}


\section{Education}
\cvitem{2021 - 2025}{\textbf{Ph.D. in Applied Mathematics.} Illinois Institute of Technology (IIT).}
\cvitem{2017 - 2021}{\textbf{Master of Data Science.} IIT. Summa cum laude.}
\cvitem{2017 - 2021}{\textbf{B.S. in Applied Mathematics, Minor in Computer Science.} IIT. Summa cum laude.}

\section{Experiences}
\cvitem{Summer 2023}{\textbf{Graduate Intern} at \textbf{Los Alamos National Laboratory.} I modeled the solution processes of PDEs with random coefficients using efficient and error aware Gaussian processes resulting in  \cite{sorokin.gp4darcy}.}
\cvitem{Summer 2022}{\textbf{Givens Associate} at \textbf{Argonne National Laboratory}. I researched methods to efficiently estimate failure probability using Monte Carlo with non-parametric importance sampling resulting in \cite{sorokin.adaptive_prob_failure_GP}.}
\cvitem{Summer 2021}{\textbf{Machine Learning Engineer} at \textbf{SigOpt, an Intel Company}. I developed novel meta-learning techniques for model-aware hyperparameter optimization resulting in \cite{sorokin.sigopt_mulch}.}
\cvitem{2018 - Present}{\textbf{Lead Developer} of \textbf{QMCPy: A Quasi-Monte Carlo Python Library.} This package provides researchers and practitioners with high quality sequence generators, automatic variable transformations, adaptive stopping criteria algorithms, and diverse use cases. See \cite{sorokin.MC_vector_functions_integrals,choi.QMC_software} or visit \itlink{qmcpy.org}{https://qmcpy.org}.}
\cvitem{Fall 2021 - Present}{\textbf{Teaching assistant} at \textbf{IIT}. Includes leading review sessions for Ph.D. qualifying exams.}
\cvitem{Fall 2022}{\textbf{Participant} in an elective course on  \textbf{AI Driven Science on Supercomputers} through \textbf{Argonne National Laboratory}. Coursework at \itlink{github.com/alegresor/ai-science-training-series}{https://github.com/alegresor/ai-science-training-series}.}

\nocite{
    sorokin.gp4darcy,
    sorokin.MC_vector_functions_integrals,
    choi.challenges_great_qmc_software,
    sorokin.adaptive_prob_failure_GP,
    sorokin.sigopt_mulch,
    choi.QMC_software,
    }
\printbibliography[title=Publications]
    
\section{Awards}
\cvitem{2023}{\textbf{Outstanding Mathematics Poster}, Los Alamos National Laboratory.}
\cvitem{2021}{\textbf{Best Manuscript}, IIT Undergraduate Research Journal.}
\cvitem{2020}{\textbf{Karl Menger Student Award for Exceptional Scholarship}, IIT.}

\section{References}
\cvitem{\href{mailto:hickernell@iit.edu}{hickernell@iit.edu}}{\textbf{Fred J. Hickernell, Ph.D.} Vice Provost for Research and Professor of Applied Mathematics, IIT.}
\cvitem{\href{mailto:nickh@lanl.gov}{nickh@lanl.gov}}{\textbf{Nicolas W. Hengartner, Ph.D.} Senior Scientist, Los Alamos National Laboratory.}
\cvitem{\href{mailto:mccourt@sigopt.com}{mccourt@sigopt.com}}{\textbf{Michael J. McCourt, Ph.D.} Research Engineer, SigOpt, an Intel Company.}
\cvitem{\href{mailto:vhebbur@anl.gov}{vhebbur@anl.gov}}{\textbf{Vishwas Rao, Ph.D.} Assistant Computational Mathematician, Argonne National Laboratory.}

%%%%% COVER LETTER
%\clearpage
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%\makelettertitle % Print letter title
%\lipsum[1-3] % Dummy text
%\makeletterclosing % Print letter signature

\end{document}